Computational Problem Set 1: Macro Data (Answers)
========================================================


```{r echo=FALSE, message=FALSE, results="hide", cache=FALSE}
library(ggplot2)
library(tables)
library(gdata)
library(knitr)
library(rdatamarket)
booktabs()

opts_chunk$set(fig.align="center",  message=FALSE, warning=FALSE)
```

Instructions: 
+ You must publish your homework on Rpubs.com before Thurdsay at 23:59 and upload a copy of your Rmd file to *your* GitHub repository. All your files must have your last name in the filename, e.g. `cps1_answer_mayer.*` .

+ Let me suggest to focus in your pure R script first, and then integrate text and code in your Rmd document.

+ There is a *starter* file in my repo. It's a good idea to get ahold of it by pull it to your local repo.

## Part I. A classic: Penn World Tables

+ Produce three plots (one per variable), showing in each plot, the corresponding time series for all your selected countries. 

```{r}
#Importar base de datos 1
db1 <- read.csv("pwt71_w_country_names.csv")
selectediso = c("GER","CAN", "GRC") ;
gcgsel=subset(db1,isocode %in% selectediso)# 
gcgsel = droplevels(gcgsel) 

#Pregunta 1
  #Gráficos
    #Para GDP per capita (PPP) $ of 2005
      # make "base" plot, will add features below
      plot1=qplot(year,rgdpch, data=gcgsel,geom= "path", colour=country)
      plot2 = plot1 + geom_smooth(se=TRUE, linetype=2)
      plot3= plot2 + labs(colour = "Countries", x="Year", y="GDP per capita (PPP), $ of 2005")
      print(plot3)

    #Para Consumption Share of PPP Converted GDP(pc) at 2005 constant prices [rgdpl]
      plot4=qplot(year,kc, data=gcgsel,geom= "path", colour=country) + geom_smooth(se=TRUE, linetype=2) + labs(colour = "Countries", x="Year", y="Consumption Share of PPP Converted GDP(pc) 2005")
      print(plot4) 

    #Para Government Consumption Share of PPP Converted GDP(pc) at 2005 constant prices [rgdpl]
      plot5=qplot(year,kg, data=gcgsel,geom= "path", colour=country) + geom_smooth(se=TRUE, linetype=2) + labs(colour = "Countries", x="Year", y="Government Consumption Share of PPP Converted GDP(pc) 2005")
      print(plot5)
```

+ Install and/or load the `tables` package. Produce a table similar to 
the first table presented in package's vignette. 

```{r}
    # now a table
    # na.omit is needed since otherwise mean and sd return NA
    table1 = tabular((country + 1) ~ (n=1) + Format(digits=2)*(kc+ki+kg+openk) * (mean+sd), data=na.omit(gcgsel))
    table1
```

## Part II. Cool new kid: Datamarket.com

+ Plot the data (in separate plots, if necessary). In fact, plot the data in three different ways. One, using `plot` with the option `plot.type="multiple`. Another one, also using `plot`, but with the option `plot.type="multiple`. A last one, using `ggplot2`'s commands. In the starter file, you may find examples for this.

```{r}
 #Para Real Effective Exchange Rate. Sources: World Bank (citing: World Bank staff calculations based on Datastream and IMF International Finance Statistics data.)
    erinfo = dminfo("http://data.is/OKBWv1")
    erzoo = dmseries(erinfo)
    erdf = dmlist(erinfo)
    
    ersmalldf =  dmlist(erinfo, "Country" = c("Australia","Belize","Uganda"))
    ersmallzoo =  dmseries(erinfo, "Country" = c("Australia","Belize","Uganda"))
    
    plot1_er=qplot(Year,Value, data=ersmalldf,geom= "path", colour=Country)
    print(plot1_er)
    
    plot(ersmallzoo, plot.type="single", lty=1:3, col=1:3)
    legend(x="bottomright",legend=colnames(ersmallzoo), lty=1:3, col=1:3)
    
    plot(ersmallzoo, plot.type="multiple")

  #Para Current Account Balance (% of GDP). Sources: World Bank (citing: International Monetary Fund, Balance of Payments Statistics Yearbook and data files, and World Bank and OECD GDP estimates.)
    cainfo = dminfo("http://data.is/Q2PnYu")
    cazoo = dmseries(cainfo)
    cadf = dmlist(cainfo)
    
    casmalldf =  dmlist(cainfo, "Country" = c("Angola","Estonia","Fiji"))
    casmallzoo =  dmseries(cainfo, "Country" = c("Angola","Estonia","Fiji"))
    
    plot1_ca=qplot(Year,Value, data=casmalldf,geom= "path", colour=Country)
    print(plot1_ca)
    
    plot(casmallzoo, plot.type="single", lty=1:3, col=1:3)
    legend(x="bottomright",legend=colnames(casmallzoo), lty=1:3, col=1:3)
    
    plot(casmallzoo, plot.type="multiple")
```

## Part III. The local credit: Using BCCh' data.

+ Repeat something similar to what you did in Part I (i.e. plot and table), but using data taken from the web site of the Banco Central de Chile.

```{r}
#Importar base de datos 2
db2 <- read.csv("tcanual.csv")

#Pregunta 3
  #Gráficos
    #Para Tipo de Cambio Nominal 
      plot6=qplot(year,tcnom, data=db2, geom= "path") + geom_smooth(se=TRUE, linetype=2) + labs(x="Año", y="Tipo de Cambio Nominal (dólar observado $/USD)")
      print(plot6)

    #Para Tipo de Cambio Real
      plot7=qplot(year,tcreal, data=db2, geom= "path") + geom_smooth(se=TRUE, linetype=2) + labs(x="Year", y="Tipo de Cambio Real (índice 1986=100)")
      print(plot7)

  #Tablas
    data2 <- matrix(c("TC_Nominal Promedio","TC_Real Promedio",mean(db2$tcnom),mean(db2$tcreal)),ncol=2,byrow=TRUE)
    table2 <- as.table(data2)
    table2
```




